---
title: "R Notebook"
output: html_notebook
---

```{r}
library("deldir")
Points1 <- data.frame(x=runif(10), y=runif(10))
Points2 <- data.frame(x=runif(100), y=runif(100))
x=Points1$x
y=Points1$y

vtess <- deldir(x, y)

plot(x, y, type="n", asp=1)
points(x, y, pch=20, col="red", cex=0.5)
points(Points2$x,Points2$y,pch=2)
plot(vtess, wlines="tess", wpoints="none", number=FALSE, add=TRUE, lty=1)
```
Otro ejemplo

```{r}
suppressMessages(library(spatstat)) 
X <- runifpoint(42)
dichX <-dirichlet(X) 
plot(dichX)
plot(X, add=TRUE)
LI <- dirichletNetwork(cells)
str(LI)

```

```{r}
library(sf)
library(dplyr)

df <- tibble::tribble(
    ~Station, ~Lat_dec, ~Long_dec, ~Surface_T,
         247, 50.33445, -2.240283,      15.19,
         245, 50.58483, -2.535217,      14.11,
         239, 50.16883,  -2.50925,      15.41,
         225, 50.32848, -2.765967,      15.34,
         229,   50.639,   -2.9648,      14.09,
         227, 50.33757, -3.303217,      15.12,
         217, 50.16657, -3.563817,      15.13,
         207, 49.66683,  -3.55655,      15.04,
         213, 50.16512, -3.824667,      14.97,
         219, 49.83707, -3.815483,      14.78
    )


#create sf object with points
stations <- st_as_sf( df, coords = c( "Long_dec", "Lat_dec" ) ) 

#create voronoi/thiessen polygons
v <- stations %>% 
  st_union() %>%
  st_voronoi() %>%
  st_collection_extract()

library(leaflet)
leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers( data = stations ) %>%
  addPolygons( data = v ) 
```

```{r}
library(rgdal)
library(tmap)

# Load precipitation data
z <- gzcon(url("http://colby.edu/~mgimond/Spatial/Data/precip.rds"))
P <- readRDS(z)

# Load Texas boudary map
z <- gzcon(url("http://colby.edu/~mgimond/Spatial/Data/texas.rds"))
W <- readRDS(z)

# Replace point boundary extent with that of Texas
P@bbox <- W@bbox

tm_shape(W) + tm_polygons() +
  tm_shape(P) +
  tm_dots(col="Precip_in", palette = "RdBu", auto.palette.mapping = FALSE,
             title="Sampled precipitation \n(in inches)", size=0.7) +
  tm_text("Precip_in", just="left", xmod=.5, size = 0.7) +
  tm_legend(legend.outside=TRUE)
```



```{r}
library(spatstat)  # Used for the dirichlet tessellation function
library(maptools)  # Used for conversion from SPDF to ppp
library(raster)    # Used to clip out thiessen polygons

# Create a tessellated surface
th  <-  as(dirichlet(as.ppp(P)), "SpatialPolygons")

# The dirichlet function does not carry over projection information
# requiring that this information be added manually
proj4string(th) <- proj4string(P)

# The tessellated surface does not store attribute information
# from the point data layer. We'll use the over() function (from the sp
# package) to join the point attributes to the tesselated surface via
# a spatial join. The over() function creates a dataframe that will need to
# be added to the `th` object thus creating a SpatialPolygonsDataFrame object
th.z     <- over(th, P, fn=mean)
th.spdf  <-  SpatialPolygonsDataFrame(th, th.z)

# Finally, we'll clip the tessellated  surface to the Texas boundaries
th.clp   <- raster::intersect(W,th.spdf)

# Map the data
tm_shape(th.clp) + 
  tm_polygons(col="Precip_in", palette="RdBu", auto.palette.mapping=FALSE,
              title="Predicted precipitation \n(in inches)") +
  tm_legend(legend.outside=TRUE)
```

# Table of shared edges for a Voronoi tesslleation

Tomado de este https://stackoverflow.com/questions/24317733/table-of-shared-edges-for-a-voronoi-tesslleation

```{r original}
library(spatstat)
points <- ppp(x=c(-77.308703, -77.256582, -77.290600,  -77.135668, -77.097144),
         y=c(39.288603, 39.147019, 39.372818, 39.401898, 39.689203),
         window=owin(xrange=c(-77.7,-77), yrange=c(39.1, 39.7)))
vt <- dirichlet(points) # Dirichlet tesselation
plot(vt)

tilesA <- tiles(vt)
n_tiles <- length(tilesA)
boundary_calcs <- data.frame('area1_id'=numeric(), 'area2_id'=numeric(), 'neighbor'=logical()) # Store boundary pairs
for (i in 1:n_tiles) {
  for (j in 1:n_tiles) {
    intersection <- intersect.owin(tilesA[[i]], tilesA[[j]], fatal=FALSE) # does not work
    if (!is.empty(intersection)) {
      boundary_calcs[nrow(boundary_calcs)+1, ] <- c(i, j, TRUE) # add to data table as new row
} } }
```
Respuesta:

```{r}
library(spatstat)
library(deldir)
points <- ppp(x=c(-77.308703, -77.256582, -77.290600,  -77.135668, -77.097144),
         y=c(39.288603, 39.147019, 39.372818, 39.401898, 39.689203),
         window=owin(xrange=c(-77.7,-77), yrange=c(39.1, 39.7)))

sharededge <- function(X) {
   verifyclass(X, "ppp")
   Y <- X[as.rectangle(X)]
   dX <- deldir(Y)
   DS <- dX$dirsgs
   xyxy <- DS[,1:4]
   names(xyxy) <- c("x0","y0","x1","y1")
   sX <- as.psp(xyxy,window=dX$rw)
   marks(sX) <- 1:nobjects(sX)
   sX <- sX[as.owin(X)]
   tX <- tapply(lengths.psp(sX), marks(sX), sum)
   jj <- as.integer(names(tX))
   ans <- data.frame(ind1=DS[jj,5], 
                     ind2=DS[jj,6], 
                     leng=as.numeric(tX))
   return(ans)
}




shared_edge_lengths <- sharededge(points)

sharededge(points)
sharededgemod(points)

x <- sharededgemod(points)


x_reverse <- x %>% select(ind1 = ind2, ind2 = ind1)

bind_rows(x, x_reverse) %>% arrange(ind1)

Y <- points[as.rectangle(points)]
dX <- deldir(Y)
dX
DS <- dX$dirsgs

```
## Hacemos prueba con otro dataframe
```{r}
df <- data.frame(x = rep(seq(1:10), 10),
                 y = rep(seq(1:10), each = 10),
                 diameter = rnorm(100, 0.3, 0.03),
                 height = rnorm(100, 0.2, 001))
W <- owin( c(0, 11), c(0,11) )
pp1 <- as.ppp( df, W = W)

test <- sharededgemod(pp1)
test
plot(dirichlet(pp1))
df

Y <- pp1[as.rectangle(pp1)]
dX <- deldir(Y)
df1 <- rownames_to_column(df) %>%
   mutate(rowname = as.integer(rowname))
dX
DS <- dX$dirsgs

left_join(test, df1, by = c("ind1" = "rowname"))
```
Todo bien pero necesito data de cada area

```{r}
sharededgemod <- function(X) {
   verifyclass(X, "ppp")
   Y <- X[as.rectangle(X)]
   dX <- deldir(Y)
   DS <- dX$dirsgs
   ans_prev <- data.frame(ind1=DS[,5], 
                     ind2=DS[,6])
   ans_reverse <- ans_prev %>% select(ind1 = ind2, ind2 = ind1)

   ans <- bind_rows(ans_prev, ans_reverse) %>% arrange(ind1)
   return(ans)
}
```

```{r}
df <- data.frame(x = rep(seq(1:10), 10),
                 y = rep(seq(1:10), each = 10),
                 diameter = rnorm(100, 0.3, 0.03),
                 height = rnorm(100, 0.2, 001))
df <- rownames_to_column(df) %>%
   mutate(rowname = as.integer(rowname))
df <- df %>% select(x,y,rowname,everything())
W <- owin( c(0, 11), c(0,11) )
pp1 <- as.ppp( df, W = W)

sharededgemod(pp1)

left_join(sharededgemod(pp1), df, by = c("ind1" = "rowname"))
```
```{r}
library(spatstat)
suppressMessages(library(tidyverse))
library(deldir)
sharededgemod <- function(X) {
   verifyclass(X, "ppp")
   Y <- X[as.rectangle(X)]
   dX <- deldir(Y)
   DS <- dX$dirsgs
   ans_prev <- data.frame(ind1=DS[,5], 
                     ind2=DS[,6])
   ans_reverse <- ans_prev %>% select(ind1 = ind2, ind2 = ind1)

   ans <- bind_rows(ans_prev, ans_reverse) %>% arrange(ind1)
   return(ans)
}

vecinos_thiessen <- function(df) {
   df <- rownames_to_column(df) %>%
      mutate(rowname = as.integer(rowname)) %>%
      select(x, y, rowname, everything())
   W <- owin(c(min(df$x)-1, max(df$x)+1), c(min(df$y)-1, max(df$y)+1))
   pp1 <- as.ppp(df, W = W)
   sharededgemod(pp1)
   left_join(sharededgemod(pp1), df, by = c("ind1" = "rowname"))
}

df <- data.frame(x = rep(seq(1:10), 10),
                 y = rep(seq(1:10), each = 10),
                 diameter = rnorm(100, 0.3, 0.03),
                 height = rnorm(100, 0.2, 001))

vecinos_thiessen(df)


df2 <- data.frame(x=c(-77.308703, -77.256582, -77.290600,  -77.135668, -77.097144),
         y=c(39.288603, 39.147019, 39.372818, 39.401898, 39.689203),
         caract = rnorm(5))

df2

vecinos_thiessen(df2)

```
## Prueba con ventana correcta

http://r.789695.n4.nabble.com/R-Calculating-Thiessen-weights-for-an-area-with-irregular-boundary-td4706201.html


(1) The manner in which you presented your data was a total mess. 
If you ask for help, please have the courtesy to present your data in 
such a manner that a potential "helper" can access it without needing to 
do a great deal of editing and processing.  Like so: 

```{r remedy001}

pts <- as.data.frame(matrix(c(415720,432795,415513,432834,415325, 
                               432740,415356,432847,415374,432858, 
                               415426,432774,415395,432811,415626, 
                               432762),ncol=2,byrow=TRUE)) 
names(pts) <- c("x","y") 

bdry <- as.data.frame(matrix(c(415491,432947,415269,432919,415211, 
                                432776,415247,432657,415533,432657, 
                                415781,432677,415795,432836,415746, 
                                432937),ncol=2,byrow=TRUE)) 
names(bdry) <- c("x","y") 

```

(2) Well, at least you presented a usable data set (even though the 
presentation was lousy) which is better than what most posters do.  And 
you asked a "partially" clear question. 

(3) I do not know what you mean by "Thiessen weights".  I am guessing 
that these are the areas of the Dirichlet tiles (Thiessen polygons), 
intersected with the "boundary polygon" (i.e. observation window). 

(4) If my guess is correct, the following should accomplish the desired 
task: 

```{r remedy002}

require(spatstat) # You will (probably) need to install spatstat first. 
W <- owin(poly=bdry) 
X <- as.ppp(pts,W=W) 
plot(X) # Just to make sure it looks right. 
dX <- dirichlet(X) 
plot(dX) # Just to make sure ..... 

```


